\textsc{Ferret Miner}: A Process Mining Case Study${}^\dagger$\thanks{${}^\dagger$~Github: \texttt{https://github.com/Martin-Chivo/CMPE255-Team8}; Google Drive: \texttt{shorturl.at/cgFIP}}

### 2022-12-14 paper/paper.tex
Edits before final submission.

Furthermore, we are very interested in the evaluation and application
of an emerging process mining approach based on
\textsc{pm4py}, a Python process mining library
developed by Berti et al.~\cite{BeZe2019}.
According to the authors,
\textsc{pm4py} is a modern, open-source, and extensible platform developed
specifically for the data science community. Prior to the turn of the
millenium,
there were hardly any tooling for process mining, but
since then a slew of software tools, both open-source
(\textsc{prom} and \textsc{apromore}) and commercial
(\textsc{disco}, \textsc{celonis}, and \textsc{processgold}),
have been developed for process mining.
Yet, many were proprietary, hard to extend,
or hidden behind graphical user interfaces.
The conservative mindset of process mining
tooling contrasted greatly with the modern philosophy of data science
R\&D,
which put significant emphasis on openness and extensibility.
\textsc{pm4py} was developed to bridge the gap
and bring process mining to mainstream data science
capabilities such as
\textsc{pandas}, \textsc{numpy}, \textsc{scikit-learn}.
We whole-heartedly
agree with the assessment of the authors, and look forward to opportunities
that the \textsc{pm4py} approach brought forth, including
the adoption of modern and rapidly evolving machine learning
techniques to process mining.

@@

We shall note that process mining is a relatively new and unfamiliar
technique, and
as such we spent a disproportional amount of time ramping up the project.
While we completely believe in the full potential of \textsc{pm4py} due to
its focus on algorithmic discovery and availability
on Python, it is
essentially still an academic software in its nascent stage, and 
hence suffers from many issues such as software instability,
limitation in visualization and presentation, scanty documentation,
and immaturity in API design.  There is still plenty of room for
improvement.

@@

The logs that were imported into Python via 
\textsc{pm4py} were converted into
dataframes, a key construct of
\textsc{pandas}, the popular Python Data Analysis Library. However, as
dataframes are not hierarchical, \textsc{pm4py} flattened the logs so that 
the enclosing case and the case attributes
became attributes of the event. If
there were $A_C$ attributes associated with a
case, and $A_E$ event attributes in the
\textsc{xes} specification, after \textsc{pm4py} import, we would obtain a
\textsc{pandas} dataframe 
with $N$ events, each with a total of $A_C + A_E$ attributes.

@@

As a result, the reimbursement process for international travel is
far more complex, and the formal specification that describes
international cases also contain more fields.
Specifically, while domestic cases only have 5 attributes
each, international cases have 13 additional attributes, on top of
the 5 attributes shared with domestic cases
(\texttt{id}, \texttt{concept:name}, \texttt{BudgetNumber},
\texttt{DeclarationNumber}, \texttt{Amount}), for a total of 18 attributes.
Regardless of the type of trips, however,
the event in the \textsc{xes} hierarchy has the same 5 attributes
(\texttt{id}, \texttt{org:resource}, \texttt{concept:name},
\texttt{time:timestamp}, and \texttt{org:role}).
After flattening, \textsc{pm4py} returned a
domestic dataframe with $56437$ events and $10~(=5+5$) attributes, and
an international dataframe with $72151$ events and $23~(=18+5$) attributes.
To avoid namespace collision, all case attributes were prefixed with
\texttt{case:} by \textsc{pm4py} (for example, the \texttt{id} field of a case
became \texttt{case:id}). Please refer to Table
\ref{table-event} for a complete list of all attributes:

\begin{table}[htbp]
\caption{XES Attributes for Events, and Domestic and Int'l Cases}
\vspace{-1em}
\begin{center}
\begin{verbatim}
  XES Event Attributes (5 Total)
    ---------------------------------------------------------
    id, org:resource, concept:name, time:timestamp, org:role
    ---------------------------------------------------------

  XES Domestic Case Attributes (5 Total)
    ---------------------------------------------------------
    id, concept:name, BudgetNumber, DeclarationNumber, Amount
    ---------------------------------------------------------

  XES International Cases (18 fields)
    ---------------------------------------------------------
    Permit travel permit number, DeclarationNumber, Amount,
    RequestedAmount, Permit TaskNumber, Permit BudgetNumber,
    OriginalAmount, Permit ProjectNumber, concept:name,
    Permit OrganizationalEntity, travel permit number,
    Permit RequestedBudget, id, Permit ID, Permit id,
    BudgetNumber, Permit ActivityNumber, AdjustedAmount        
    ---------------------------------------------------------
\end{verbatim}
\end{center}
\vspace{-1em}
\label{table-event}
\end{table}

@@

While we did not find any missing value per se (as far
as \textsc{pandas} is concerned), we did find columns with string values
\textsc{unknown} or \textsc{missing}. We
carefully evaluated what to do with these attributes on a case-by-case
basis. For example, we could drop the column (attribute), drop the row
(event), fill the missing values, or simply ignore the column.

@@

As a result of these cleaning procedures, the size of the
the international dataframe was reduced from 72151 to 43707 (a 60\% drop),
with the
missing permit accounting for 95\% of such reduction. The number of
columns was reduced from 23 to 19, since we dropped
several permit-related columns that are duplicates.
Similarly, the domestic dataframe was also modified to a much small extent.
The number of events was reduced from 55087, a mere 2\% drop, and the
number of columns stayed the same.

@@

Process models that can explain all possible event traces could be
arbitrarily complex. For example, obviously we would expect reimbursement to
be paid out only after the request was approved. But what if there is
a trace with a missing approval due to erroneous logging? A process model
built to handle 100\% of traces must handle a flow with
payment before request, however bizzare such trace is.
Not only would the model be more complex and unwieldy,
it would also be incorrect and fail our objective.

A naive approach would be to remove events that are uncommon, but doing so may
not be sufficient. Consider the previous example;
while \textsc{request approved} that happened after \textsc{payment handled}
might be a rare sequence, neither of these events were rare.

In \textsc{pm4py} terminology, the variants of an event log is the
union of all possible sequences of event execution (ignoring all but the
event labels). For example, there were
68 variants in the domestic log, and 464 variants in the international log.
In fact, the above example
points to the need to remove traces that are uncommon. Clearly, it could
be beneficial to have the choice to build the process model based on
only the most popular traces. Indeed, this was an important part of our
methodology and we shall take a closer look in the next section.

@@

We must first answer the
question of what formal model to use. Our choices include \textsc{bpmn}\footnote{\textsc{bpmn} stands for Business Process Model Notation}  model,
process tree, \textsc{petri net}, and Directly-Follows Graph (\textsc{dfg}). The
first three are mathematically equivalent and inter-changeable. On the other
hand, \textsc{dfg} shows a different view of \textsc{bpmn} graph constructed by aggregrating all possible link
between any pair of events that follows each other.

There are pros and cons in choosing \textsc{petri net} vs \textsc{dfg}. \textsc{dfg}s can be constructed
directly from the event logs, and are simple to understand. \textsc{petri net}s (as well
as the equivalents) can only be generated heuristically, for example, 
through inductive or heuristics miners (which \textsc{pm4py} supports).
The difference mainly lies on how concurrency is handled. For example,
say there are two activities $X$ and $Y$ that are sandwiched between
$A$ and $B$. In other words, the following are both legitimate sequence
of executions:

@@

While both \textsc{alpha miner} and \textsc{inductive miner} would correctly deduct
(probabilistically) that $X$ and $Y$ have no inter-dependency but are
instead concurrent events, \textsc{dfg} would not be able to discern that, because
all it saw was $Y$ directly follows $X$ in the first example, and
$X$ directly follows $Y$ in the second. Thus, concurrency would
show up in \textsc{dfg}s as tight loops between two activities, yet there is no
way to prove that tight loops imply concurrency. If indeed \textsc{dfg}s
become too complicated, they will confuse rather than aide reasoning.

For our purpose, however, we still believe 
is the preferred approach as the statistics on the edges of a \textsc{dfg} can be
made readily available, and more easily reasoned with. We just need to make
sure we have a model that is not too complicated.
This speaks to the importance of limiting the model size, which we shall
discuss next.

@@

How many top variants do we use to build the model?
We did experiment with different values of $k$, where $k$ is the number of
top variants to be used to build the \textsc{dfg}. We
evaluated many factors, though more qualitatively than otherwise,
and came to the conclusion
that we would achieve the best balance between coverage and robustness if
we keep approximately 15 to 25\% of the top variants, depending on data
(higher for domestic, and lower for international). Figures~\ref{fig-domestic}
and \ref{fig-international} shows the \textsc{dfg} models we picked for
domestic and international reimbursement respectively. In each figure,
the \textsc{dfg} to the left is annotated with the number of directly following
edges, and the \textsc{dfg} to the right is annotated with the mean duration between
the two events. Both models captured the vast majority of the important
interactions very well and were reasonably easy to comprehend.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.60\textwidth]{images/domestic.png}}
\caption{\textsc{dfg} Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}
\vspace{-1em}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.60\textwidth]{images/international.png}}
\caption{\textsc{dfg} Model for International Reimbursement.}
\label{fig-international}
\end{figure*}
\vspace{-1em}

@@

The biggest bottleneck is the supervisor activities for both international
and domestic declarations.  For the supervisor to do the final approval and
request payment, it takes an average of 4 to 5 days.
To find such bottleneck, we would identify that
links with both high frequency \textit{and} long duration. Since the models
are simple enough, we were able to visually inspect the models and identify
such link. We did add code to work around \textsc{pm4py} and
automatically identify such links.

On the other hand, if we
were to identify one activity, \textsc{Payment Handled}
is the biggest bottleneck. That said,
it might be outside of the organization’s control and may be more of a
financial institution issue.

@@

This can be done with a method called token-based replay (\textsc{tbr}) on the
\textsc{petri net} converted from the process model. For each trace, we would try
to see if it can be simulated on the \textsc{petri net} which can be done
precisely in a mathematically sound
way. We define the total fitness
simply as the percentage of traces that fit the model. Other techniques
we can apply are 
alignment analysis and behavior analysis, though
they both come at the expense of higher runtime complexity.
Together these techniques can be used to better identify the hows and whys of
non-conformance, and to build better models.
In conformance analysis,
getting to 100\% total fitness is not a desired goal, as explained earlier.
Instead, what we seek is a tradeoff. On the one hand, you want the model
to be robust enough to elegantly explain the process. On the other hand,
we do not want to over-build a model so complex that it is impossible to
reason about.

Let's use our specific problem as an example. We
ran an experiment to examine the tradeoff between fitness and model
complexity. We built the model multiple times with \textsc{inductive miner},
each time on a different value of $k$, where $k$ is the number of top
variants we
used to build the model, and we recorded the total fitness via conformance
check, as well as an estimate the complexity of the model computed using
custom Python code.
In Figure~\ref{fig-tradeoff}, the
red line is the total fitness, and the blue line is the size of the
model. We see that, as we include more top variants, the model gets more
complex, but the fitness also improves. If we would include only the top
3 variants, we can already explain 90\% of the traces. But if we blindly
crank up the knob to 
18 variants, the model would now account for 99\% of the traces, but the
it is 5 times bigger, and much harder to understand.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.40\textwidth]{images/tradeoff.png}}
\caption{Fitness and Complexity vs Top $k$ Variants.}
\label{fig-tradeoff}
\end{figure}

The sweat spots happen at $k = 5$, which can explain 96\% of the traces.
Moreover,
it was able to properly capture the submission, approval, rejection,
resubmission, and the final payment. It represents the best tradeoff
between fitness and model complexity. It would be interesting to further
expand the idea of conformance checking as a way to help build the model,
and we have only just scratched the surface.

@@

Another area of interest is to apply machine learning techniques to
perform (1) flow analysis to predict likelihood of resubmission,
rejection, payment delay, or over-budget based on other variables (time
since submission, request amount, prior owner approval), and (2) timing
analysis to determine the average expected time before the trace completes.
This provides
important clues to administrators and employees alike about the time
frame of payment in the best-case scenario. We are also interested in
detecting non-compliance \textit{as it happens} and sending alerts to
administrators.

@@

\item
\textbf{Carlos Hernandez} -- wrote the first draft of the term paper,
completed with extensive literature survey, project outline,
report template, as well as a significant portion of the writeup.

\item
\textbf{Hardy Leung} -- did an early investigation on \textsc{pm4py}, and
worked on conformance analysis. He also migrated the paper to the IEEE
template, and wrote the second half of the term paper.

>>>>

Furthermore, we are very interested in the evaluation and application
of an emerging process mining approach based on
\textsc{pm4py}, a \textsc{python} process mining library
developed by Berti et al.~\cite{BeZe2019}.
According to the authors,
\textsc{pm4py} is a modern, open-source, and extensible platform developed
specifically for the data science community. Prior to the turn of the
millenium,
there were hardly any tooling for process mining, but
since then a slew of software tools, both open-source
(\textsc{prom} and \textsc{apromore}) and commercial
(\textsc{disco}, \textsc{celonis}, and \textsc{processgold}),
have been developed for process mining.
Yet, many were proprietary, hard to extend,
or hidden behind graphical user interfaces.
The conservative mindset of process mining
tooling contrasted greatly with the modern philosophy of data science
R\&D,
which put significant emphasis on openness and extensibility.
\textsc{pm4py} was developed to bridge the gap
and bring process mining to mainstream data science
capabilities such as
\textsc{pandas}, \textsc{numpy}, \textsc{scikit-learn}.
We whole-heartedly
agree with the assessment of the authors, and look forward to opportunities
that the \textsc{pm4py} approach brought forth, including
the adoption of modern and rapidly evolving machine learning
techniques to process mining.

@@

We shall note that process mining is a relatively new and unfamiliar
technique, and
as such we spent a disproportional amount of time ramping up the project.
While we completely believe in the full potential of \textsc{pm4py} due to
its focus on algorithmic discovery and availability
on \textsc{python}, it is
essentially still an academic software in its nascent stage, and 
hence suffers from many issues such as software instability,
limitation in visualization and presentation, scanty documentation,
and immaturity in API design.  There is still plenty of room for
improvement.

@@

The logs that were imported into \textsc{python} via 
\textsc{pm4py} were converted into
dataframes, a key construct of
\textsc{pandas}, the popular Python Data Analysis Library. However, as
dataframes are not hierarchical, \textsc{pm4py} flattened the logs so that 
the enclosing case and the case attributes
became attributes of the event. If
there were $A_C$ attributes associated with a
case, and $A_E$ event attributes in the
\textsc{xes} specification, after \textsc{pm4py} import, we would obtain a
\textsc{pandas} dataframe 
with $N$ events, each with a total of $A_C + A_E$ attributes.

@@

As a result, the reimbursement process for international travel is
far more complex, and the formal specification that describes
international cases also contain more fields.
Specifically, while domestic cases only have 5 attributes
each, international cases have 13 additional attributes, on top of
the 5 attributes shared with domestic cases
(\texttt{id}, \texttt{concept:name}, \texttt{BudgetNumber},
\texttt{DeclarationNumber}, \texttt{Amount}), for a total of 18 attributes.
Regardless of the type of trips, however,
the event in the \textsc{xes} hierarchy has the same 5 attributes
(\texttt{id}, \texttt{org:resource}, \texttt{concept:name},
\texttt{time:timestamp}, and \texttt{org:role}).
After flattening, \textsc{pm4py} returned a
domestic dataframe with $56437$ events and $10~(=5+5$) attributes, and
an international dataframe with $72151$ events and $23~(=18+5$) attributes.
To avoid namespace collision, all case attributes were prefixed with
\texttt{case:} by \textsc{pm4py} (for example, the \texttt{concept:name} field of a case
became \texttt{case:concept:name}). Please refer to Table
\ref{table-event} for a complete list of all attributes:

\begin{table}[htbp]
\caption{XES Attributes for Events, and Domestic and Int'l Cases}
\vspace{-1em}
\begin{center}
\begin{verbatim}
  XES Event Attributes (5 Total)
    ----------------------------------------------------------
    id, org:resource, concept:name, time:timestamp, org:role
    ----------------------------------------------------------

  XES Domestic Case Attributes (5 Total)
    ----------------------------------------------------------
    id, concept:name, BudgetNumber, DeclarationNumber, Amount
    ----------------------------------------------------------

  XES International Cases (18 fields)
    ----------------------------------------------------------
    id, concept:name, BudgetNumber, DeclarationNumber, Amount,
    Permit travel permit number, RequestedAmount,
    Permit TaskNumber, Permit BudgetNumber, OriginalAmount,
    Permit ProjectNumber, Permit OrganizationalEntity,
    travel permit number, Permit RequestedBudget, Permit ID,
    Permit id, Permit ActivityNumber, AdjustedAmount        
    ----------------------------------------------------------
\end{verbatim}
\end{center}
\vspace{-1em}
\label{table-event}
\end{table}

@@

While we did not find any missing value \textit{per se} as far
as \textsc{pandas} is concerned, we did find columns with string values
\textsc{unknown} or \textsc{missing}. We
carefully evaluated what to do with these attributes on a case-by-case
basis. For example, we could drop the column (attribute), drop the row
(event), fill the missing values, or simply ignore the column.

@@

As a result of these cleaning procedures, the size of the
the international dataframe was reduced from 72151 to 43707 (a 60\% drop),
with the
missing permit accounting for 95\% of such reduction. The number of
columns was reduced from 23 to 19, since we dropped
several permit-related columns that are duplicates.
Similarly, the domestic dataframe was also modified, but to a much small extent.
The number of events was reduced from 55087, a mere 2\% drop, and the
number of columns stayed the same.

@@

Process models that can explain all possible event traces could be
arbitrarily complex. For example, obviously we would expect reimbursement to
be paid out only after the request was approved. But what if there is
a trace with completed payment that was approved only after the fact?
A process model
built to handle 100\% of traces must handle a sequence with
payment before approval, however bizzare that may be.
Not only would the model be more complex and unwieldy,
it would also be incorrect and fail our objective.

A naive approach would be to remove events that are uncommon, but doing so
would not be sufficient. Consider the previous example;
while \textsc{request approved} that happened after \textsc{payment handled}
might be a rare sequence, neither of these events were rare.

In \textsc{pm4py} terminology, the variants of an event log is the
union of all possible sequences of event \textit{labels}.
For example, there were
68 variants in the domestic log, and 464 variants in the international log.
In fact, the above example
points to the benefit of building the process model based on
only the most popular traces.  Indeed, this was an important part of our
methodology and we shall take a closer look in the next section.

@@

We must first answer the
question of what formal model to use. Our choices include 
the \textsc{bpmn} model,
process tree, \textsc{petri net}, and Directly-Follows Graph (\textsc{dfg}). The
first three are mathematically equivalent and inter-changeable. On the other
hand, \textsc{dfg} shows a different view of \textsc{bpmn} graph constructed by aggregrating all possible links
between any pair of events that follows each other.

There are pros and cons in choosing \textsc{petri net} vs \textsc{dfg}. \textsc{dfg}s can be constructed
directly from the event logs, and are simple to understand. \textsc{petri net}s (as well
as the equivalents) can only be generated heuristically, for example, 
through \textsc{alpha miner} or \textsc{heuristics miner}.
The difference mainly lies in how concurrency is handled. For example,
say there are two concurrent
activities $X$ and $Y$ that are sandwiched between
$A$ and $B$. In other words, the following are both legitimate sequence
of executions:

@@

While both \textsc{alpha miner} and \textsc{inductive miner} would correctly deduct
(probabilistically) that $X$ and $Y$ have no inter-dependency but are
instead concurrent events, \textsc{dfg} would not be able to discern that, because
all it saw was $Y$ directly follows $X$ in the first example, and
$X$ directly follows $Y$ in the second. Thus, concurrency would
show up in \textsc{dfg}s as tight loops between two activities, yet there is no
way to prove that tight loops imply concurrency. \textsc{dfg}s tend
to become too complicated very quickly as the model size increases,
causing confusion and providing no insight.

For our purpose, however, we still believe  \textsc{dfg}
is the preferred approach as the statistics on the edges of a \textsc{dfg} can be
made readily available, and more easily reasoned with. We do need to make
sure the model sizes are limited, which
we shall
discuss next.

@@

How many top variants do we use to build the model?
We did experiment with different values of $k$, where $k$ is the number of
top variants to be used to build the \textsc{dfg}. We
evaluated many factors, though more qualitatively than otherwise,
and came to the conclusion
that the best balance between coverage and robustness is achieved if
we kept approximately 15 to 25\% of the top variants, depending on the data
(higher for domestic, and lower for international). Figures~\ref{fig-domestic}
and \ref{fig-international} shows the \textsc{dfg} models we picked for
domestic and international reimbursement respectively. In each figure,
the \textsc{dfg} to the left is annotated with the number of directly following
edges, and the \textsc{dfg} to the right is annotated with the mean duration between
the two events. Both models captured the vast majority of the important
interactions very well and were reasonably easy to comprehend.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.55\textwidth]{images/domestic.png}}
\caption{\textsc{dfg} Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.55\textwidth]{images/international.png}}
\caption{\textsc{dfg} Model for International Reimbursement.}
\label{fig-international}
\end{figure*}

@@

The biggest bottleneck is the supervisor activities for both international
and domestic declarations.  For the supervisor to complete
 the final approval and
request payment, it takes an average of 4 to 5 days.
To find such bottleneck, we would identify that
links with both high frequency \textit{and} long duration. Since the models
are simple enough, we were able to visually inspect the models and identify
such link.
More recently, we were able to partially automate
such functionality by examining the dataframes directly, though it would be
preferable to do so within \textsc{pm4py}.

On the other hand, if we
were to identify one activity, \textsc{payment handled}
is the biggest bottleneck. However,
it might be outside of the organization’s control and may be more of a
financial institution issue.

@@

This can be done with a method called token-based replay on the
\textsc{petri net} converted from the process model. We would simulate
each trace on the \textsc{petri net} which can be done
in a precise and mathematically sound
way. We define the total fitness
simply as the percentage of traces that fit the model. Other techniques
we can apply are 
alignment analysis and behavior analysis, though
they both come at the expense of higher runtime complexity.
Together these techniques can be used to better identify the
\textit{hows} and \textit{whys} of
non-conformance, and to build better models.

In conformance analysis,
getting to 100\% total fitness is not necessarily
a desired goal, as explained earlier.
Instead, what we seek is a tradeoff. On the one hand, we want the model
to be robust enough to elegantly explain the process. On the other hand,
we do not want to over-build a model so complex that it is impossible to
reason about.

Let's use our specific problem as an example. We
ran an experiment to examine the tradeoff between total fitness and model
complexity. We built the model multiple times with \textsc{inductive miner},
each time on a different value of $k$, where $k$ is the number of top
variants we
used to build the model, and we recorded the total fitness via conformance
check, as well as an estimate of the model complexity computed using
custom \textsc{python} code.
In Figure~\ref{fig-tradeoff}, the
red line is the total fitness, and the blue line is the size of the
model. We see that, as we include more top variants, the model gets more
complex, but the fitness also improves. If we would include only the top
3 variants, we can already explain 90\% of the traces. But if we blindly
crank up the knob to 
18 variants, the model would now account for 99\% of the traces, but
it is also 5 times bigger, and much harder to understand.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.46\textwidth]{images/tradeoff.png}}
\caption{Fitness and Complexity vs Top $k$ Variants.}
\label{fig-tradeoff}
\end{figure}

The sweet spot happens at $k = 5$, which can explain 96\% of the traces.
Moreover,
it was able to properly capture the submission, approval, rejection,
resubmission, and the final payment. It represents the best tradeoff
between fitness and model complexity. It would be interesting to further
expand the idea of conformance checking as a way to help build the model,
and we have only just scratched the surface.

@@

Another area of interest is to apply machine learning techniques to
perform (1) flow analysis to predict likelihood of resubmission,
rejection, payment delay, or over-budget based on other variables (time
since submission, request amount, prior owner approval), and (2) timing
analysis to determine the average expected time before the trace completes.
This provides
important clues to administrators and employees alike about the time
frame of payment in the best-case scenario. We are also interested in
detecting non-compliance \textit{as it happens} and sending alerts to
administrators. The availability of many data science and machine learning
tools on \textsc{python} certainly makes these future works with
\textsc{pm4py} much more plausible.

@@

\item
\textbf{Carlos Hernandez} -- wrote the initial draft of the term paper,
completed with extensive literature survey, project outline,
report template, as well as a significant portion of the writeup.

\item
\textbf{Hardy Leung} -- did an early investigation on \textsc{pm4py}, and
worked on conformance analysis. He also migrated the paper to the IEEE
template, and wrote the majority of this paper.
